Errata

### 2025-04-03 tex/Manuscript-2.tex
Update dissertation files and fix auxiliary file counters

Biocrusts, complex communities of organisms, significantly alter surface and sub-surface processes, including water infiltration, and the cycling of carbon (C) and nitrogen (N). While their importance is recognized, studies across broad climatic gradients are scarce. We conducted rainfall simulation experiments at four sites along a 910 km Chilean Coastal Range transect, representing coastal and inland semi-arid, mediterranean, and humid climates. We quantified overland flow, sediment discharge, and fluxes of C and N in percolating water, comparing paired biocrust-covered and bare soil surfaces. Our findings reveal that biocrusts, compared to bare soil, significantly increased cumulative infiltration rates across all climates, indicating enhanced saturated hydraulic conductivity. Biocrust presence reduced runoff by 73% in humid climates and sediment flux by 80% in inland semi-arid climates. On average, soil erosion was reduced by up to 69%. Additionally, biocrusts significantly reduced C loss via erosion. Dissolved organic carbon and nitrogen fluxes were also strongly influenced by the presence of biocrusts. Overall, our study demonstrates that, though the presence of biocrust significantly reduced erosion, water and nutrient dynamic are strongly influence by its presence and the climates, showing that biocrusts act as climate-dependent regulators of crucial surface and sub-surface transport processes.

@@

Along with their ability to modify water and sediment fluxes, biocrust communities significantly shape carbon (C) and nitrogen (N) cycles. Many researchers point biocrusts as one of the most important factors that initially influence soil organic carbon (SOC) in the uppermost soil horizon before higher plants appear (Belnap et al., 2007). Furthermore, Young et al. (2022) demonstrated that biocrusts facilitate the vertical movement of soluble carbon and nutrients from the surface to subsurface mineral soils, thereby enhancing overall carbon sequestration. The significance of biocrusts in the carbon cycle extends beyond their local role in building SOC (Witzgall et al., 2024) , with these communities estimated to account for 7% of total net carbon uptake and 50% of terrestrial nitrogen fixation (Elbert et al., 2012). They further enhance C fixation through photosynthetic sequestration (Belnap et al., 2016; Grote et al., 2010). An increase in soil aggregate stability hinders C discharge by erosion (Riveras-Muñoz et al., 2022; Xiao et al., 2022), enhances soil fertility (Kheirfam et al., 2017), and fosters the establishment of other vascular and non-vascular organisms, further increasing C storage potential (Molina-Montenegro et al., 2016). In disturbed temperate forests, Gall et al. (2024) found that mosses significantly influence the relocation of SOC and total N via soil erosion and percolation, further highlighting biocrusts’ impact on nutrient redistribution. Additionally, biocrusts play an active role in the N cycle as they are responsible for approximately 40 to 85 % of N fixation worldwide, mainly through the activity of cyanobacteria , enhances soil fertility (Kheirfam et al., 2017), and foster the establishment of other vascular and non-vascular organisms, further increasing C storage potential (Molina-Montenegro et al., 2016). Additionally, biocrusts play an active role in the N cycle as they are responsible for approximately 40 to 85 % of N fixation worldwide, mainly through the activity of cyanobacteria (Rodríguez‐Caballero et al., 2018; Samolov et al., 2020). As for C, biocrusts immobilize N by incorporating it into their biomass, thereby reducing losses by leaching or volatilization (Nevins et al., 2020; Pan et al., 2021). Furthermore, biocrusts can mineralize N from SOC, making it available to other organisms in the soil ecosystem (Weber et al., 2015).

All these properties of biocrusts impact soil erosion, a central process that shapes the Earth’s surface (Luetzenburg et al., 2020; Scholten and Seitz, 2019). Water-induced erosion occurs in humid and semi-humid regions (Gholzom and Gholami, 2012; Khaleghi and Varvani, 2018) but also occurs in arid environments due to rare extreme rainfall events (Hu et al., 2022). Biocrusts not only influence infiltration and overland flow, but also form a physical barrier against erosive agents, partially absorbing the kinetic energy of running water and falling raindrops. A reduction of runoff by 25.6% and sediment discharge by 75.5% was observed when comparing runoff plots with biocrust cover below 10% and above 50% in early successional subtropical forests (Seitz et al., 2017). Similar effects of biocrusts on soil erosion have been reported in arid (Bowker et al., 2018; Eldridge et al., 2021), temperate (Gall et al., 2022a) and humid environments (Guo et al., 2022; Zhao et al., 2014). Another process of land surface stabilisation by biocrusts is the formation of aggregates from organic and mineral particles through the secretion of bacterial metabolites such as exo- and lipopolysaccharides (Costa et al., 2018; Tourney and Ngwenya, 2014; Xiao et al., 2022). Further, the trapping of soil particles within the structures of biocrusts helps prevent soil erosion (Riveras-Muñoz et al., 2022; Rodriguez et al., 2024; Xiao et al., 2022).

@@

Our findings reveal that biocrusts play a critical role in modulating associated with erosion, runoff, and percolation across varying climatic conditions (Table 1 and 2). Overall, the time required to start runoff was significantly longer in NA, with the shortest time observed in the coastal arid site, SG. Biocrusts significantly delayed runoff initiation by 97.7%, mainly due to increased surface roughness. This delay was more pronounced in NA, where the combination of enhanced roughness and high infiltration capacity extended the time for runoff initiation by three to four times. However, these effects did not extend to the subsoil, as biocrust had no measurable impact on the time needed for percolation to start.

The total runoff volume was significantly higher in SG compared to the other sites. Biocrust contributed to a significant reduction of the runoff volume, averaging a 28.0% reduction, corresponding to a significant 50.0% reduction in percolation. Regarding site-specific effects, biocrusts significantly reduced the runoff volume by 72.4% in NA. Contrarily, a contrasting trend in LC was observed, with a 36.4% increase in runoff volume associated with the biocrust presence.

The climatic gradient significantly influenced the total sediment transported by runoff, decreasing sediment mobilization as humidity increased. Biocrusts were pivotal in reducing sediment transport via runoff, resulting in an overall decrease of 69.9%. However, this reduction in runoff-associated sediment transport was accompanied by a 28.3% increase in the sediment mobilization via percolation. The interaction between the study site and biocrust presence showed significant sediment reductions across the northern sites, with NA exhibiting a similar trend, albeit without statistical significance.

The sediment load in the runoff, measured as sediment concentration in water, was significantly reduced by an average of 60.9% in the presence of biocrust. In contrast, sediment concentration in percolation increased significantly by 58.3%, highlighting a shift in sediment dynamics influenced by biocrust interactions across the study sites.

>>>>

Biocrusts, complex communities of organisms, significantly alter surface and sub-surface processes, including water infiltration, and the cycling of carbon (C) and nitrogen (N). While their importance is recognized, studies across broad climatic gradients are scarce. We conducted rainfall simulation experiments at four sites along a 910 km Chilean Coastal Range transect, representing coastal and inland semi-arid, mediterranean, and humid climates. We quantified overland flow, sediment discharge, and fluxes of C and N in percolating water, comparing paired biocrust-covered and bare soil surfaces. Our findings reveal that biocrusts, compared to bare soil, significantly increased cumulative infiltration rates across all climates, indicating enhanced saturated hydraulic conductivity. Biocrust presence reduced runoff by 73\% in humid climates and sediment flux by 80\% in inland semi-arid climates. On average, soil erosion was reduced by up to 69\%. Additionally, biocrusts significantly reduced C loss via erosion. Dissolved organic carbon and nitrogen fluxes were also strongly influenced by the presence of biocrusts. Overall, our study demonstrates that, though the presence of biocrust significantly reduced erosion, water and nutrient dynamic are strongly influence by its presence and the climates, showing that biocrusts act as climate-dependent regulators of crucial surface and sub-surface transport processes.

@@

Along with their ability to modify water and sediment fluxes, biocrust communities significantly shape carbon (C) and nitrogen (N) cycles. Many researchers point biocrusts as one of the most important factors that initially influence soil organic carbon (SOC) in the uppermost soil horizon before higher plants appear (Belnap et al., 2007). Furthermore, Young et al. (2022) demonstrated that biocrusts facilitate the vertical movement of soluble carbon and nutrients from the surface to subsurface mineral soils, thereby enhancing overall carbon sequestration. The significance of biocrusts in the carbon cycle extends beyond their local role in building SOC (Witzgall et al., 2024) , with these communities estimated to account for 7\% of total net carbon uptake and 50\% of terrestrial nitrogen fixation (Elbert et al., 2012). They further enhance C fixation through photosynthetic sequestration (Belnap et al., 2016; Grote et al., 2010). An increase in soil aggregate stability hinders C discharge by erosion (Riveras-Muñoz et al., 2022; Xiao et al., 2022), enhances soil fertility (Kheirfam et al., 2017), and fosters the establishment of other vascular and non-vascular organisms, further increasing C storage potential (Molina-Montenegro et al., 2016). In disturbed temperate forests, Gall et al. (2024) found that mosses significantly influence the relocation of SOC and total N via soil erosion and percolation, further highlighting biocrusts’ impact on nutrient redistribution. Additionally, biocrusts play an active role in the N cycle as they are responsible for approximately 40 to 85\% of N fixation worldwide, mainly through the activity of cyanobacteria , enhances soil fertility (Kheirfam et al., 2017), and foster the establishment of other vascular and non-vascular organisms, further increasing C storage potential (Molina-Montenegro et al., 2016). Additionally, biocrusts play an active role in the N cycle as they are responsible for approximately 40 to 85\% of N fixation worldwide, mainly through the activity of cyanobacteria (Rodríguez‐Caballero et al., 2018; Samolov et al., 2020). As for C, biocrusts immobilize N by incorporating it into their biomass, thereby reducing losses by leaching or volatilization (Nevins et al., 2020; Pan et al., 2021). Furthermore, biocrusts can mineralize N from SOC, making it available to other organisms in the soil ecosystem (Weber et al., 2015).

All these properties of biocrusts impact soil erosion, a central process that shapes the Earth’s surface (Luetzenburg et al., 2020; Scholten and Seitz, 2019). Water-induced erosion occurs in humid and semi-humid regions (Gholzom and Gholami, 2012; Khaleghi and Varvani, 2018) but also occurs in arid environments due to rare extreme rainfall events (Hu et al., 2022). Biocrusts not only influence infiltration and overland flow, but also form a physical barrier against erosive agents, partially absorbing the kinetic energy of running water and falling raindrops. A reduction of runoff by 25.6\% and sediment discharge by 75.5\% was observed when comparing runoff plots with biocrust cover below 10\% and above 50\% in early successional subtropical forests (Seitz et al., 2017). Similar effects of biocrusts on soil erosion have been reported in arid (Bowker et al., 2018; Eldridge et al., 2021), temperate (Gall et al., 2022a) and humid environments (Guo et al., 2022; Zhao et al., 2014). Another process of land surface stabilisation by biocrusts is the formation of aggregates from organic and mineral particles through the secretion of bacterial metabolites such as exo- and lipopolysaccharides (Costa et al., 2018; Tourney and Ngwenya, 2014; Xiao et al., 2022). Further, the trapping of soil particles within the structures of biocrusts helps prevent soil erosion (Riveras-Muñoz et al., 2022; Rodriguez et al., 2024; Xiao et al., 2022).

@@

Our findings reveal that biocrusts play a critical role in modulating associated with erosion, runoff, and percolation across varying climatic conditions (Table 1 and 2). Overall, the time required to start runoff was significantly longer in NA, with the shortest time observed in the coastal arid site, SG. Biocrusts significantly delayed runoff initiation by 97.7\%, mainly due to increased surface roughness. This delay was more pronounced in NA, where the combination of enhanced roughness and high infiltration capacity extended the time for runoff initiation by three to four times. However, these effects did not extend to the subsoil, as biocrust had no measurable impact on the time needed for percolation to start.

The total runoff volume was significantly higher in SG compared to the other sites. Biocrust contributed to a significant reduction of the runoff volume, averaging a 28.0\% reduction, corresponding to a significant 50.0\% reduction in percolation. Regarding site-specific effects, biocrusts significantly reduced the runoff volume by 72.4\% in NA. Contrarily, a contrasting trend in LC was observed, with a 36.4\% increase in runoff volume associated with the biocrust presence.

The climatic gradient significantly influenced the total sediment transported by runoff, decreasing sediment mobilization as humidity increased. Biocrusts were pivotal in reducing sediment transport via runoff, resulting in an overall decrease of 69.9\%. However, this reduction in runoff-associated sediment transport was accompanied by a 28.3\% increase in the sediment mobilization via percolation. The interaction between the study site and biocrust presence showed significant sediment reductions across the northern sites, with NA exhibiting a similar trend, albeit without statistical significance.

The sediment load in the runoff, measured as sediment concentration in water, was significantly reduced by an average of 60.9\% in the presence of biocrust. In contrast, sediment concentration in percolation increased significantly by 58.3\%, highlighting a shift in sediment dynamics influenced by biocrust interactions across the study sites.

  % --- Table 1 Code (Runoff Fluxes) ---
\begin{table}[htbp] % Changed from sidewaystable
    \centering
    \footnotesize % Reduced font size for the table
    \sisetup{separate-uncertainty = true, table-align-uncertainty = true}
    \begin{threeparttable}
      \caption{Surface runoff fluxes on the study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover. Values correspond to mean $\pm$ standard deviation (SD) of five field replicates. A letter-based display of Šidák correction accompanies surface runoff parameters\tnote{a}, and the significance of the studied factors is shown as a p-value and list of covariates (C\textsubscript{T}, N\textsubscript{T}: total carbon and nitrogen content). Different letters indicate statistically significant different values based on our data, ns: non-significant.}
      \label{tab:runoff_fluxes}
      \setlength{\tabcolsep}{3pt} % Reduced further slightly

      \begin{tabular}{@{} l l S[table-format=3.1, table-figures-uncertainty=4] @{\,} c
                             S[table-format=2.0, table-figures-uncertainty=2] @{\,} c
                             S[table-format=3.0, table-figures-uncertainty=3] @{\,} c
                             S[table-format=2.1, table-figures-uncertainty=3] @{\,} c
                          @{}}
        \toprule
        \multicolumn{2}{@{}l}{\multirow{3}{*}{\textbf{Factor}}} &
        {\makecell{\textbf{Time to}\\\textbf{start}\\\textbf{runoff}}} & & % Added line break for width
        {\makecell{\textbf{Runoff}}} & &
        {\makecell{\textbf{Sediment}\\\textbf{in runoff}}} & & % Added line break
        {\makecell{\textbf{Sediment}\\\textbf{load of}\\\textbf{runoff}}} & \\ % Added line breaks
        \cmidrule(lr){3-3} \cmidrule(lr){5-5} \cmidrule(lr){7-7} \cmidrule(lr){9-9}
        \multicolumn{2}{@{}l}{} & {[\si{\second}]} & & {[\si{L.h^{-1}}]} & & {[\si{g.m^{-2}.h^{-1}}]} & & {[\si{g.L^{-1}.m^{-2}}]} & \\
        \midrule
        \multicolumn{2}{@{}l}{\textbf{Mean} $\pm$ \textbf{SD}} & & & & & & & & \\
        & Site \quad SG  & 65.1 \pm 20.7 & {(a)}  & 49 \pm 18 & {(b)}  & 617 \pm 473 & {(c)}  & 12.1 \pm 7.9 & {(a)} \\
        & \phantom{Site \quad} QdT & 78.7 \pm 30.4 & {(a)}  & 40 \pm 16 & {(a)}  & 398 \pm 459 & {(b)}  & 9.6 \pm 9.6 & {(a)} \\
        & \phantom{Site \quad} LC  & 83.5 \pm 56.0 & {(a)}  & 39 \pm 22 & {(a)}  & 241 \pm 293 & {(b)}  & 7.3 \pm 8.8 & {(a)} \\
        & \phantom{Site \quad} NA  & 236.7 \pm 273.0 & {(b)} & 44 \pm 43 & {(a)}  & 28 \pm 44 & {(a)}   & 3.0 \pm 14.0 & {(a)} \\
        \addlinespace
        & Biocrust \quad BSC+ & 154.0 \pm 211.5 & {(b)} & 36 \pm 21 & {(a)}  & 149 \pm 222 & {(a)}  & 4.5 \pm 10.4 & {(a)} \\
        & \phantom{Biocrust \quad} BSC-- & 77.9 \pm 33.8 & {(a)}  & 50 \pm 31 & {(b)}  & 495 \pm 492 & {(b)}  & 11.5 \pm 10.0 & {(b)} \\
        \midrule
        \multicolumn{2}{@{}l}{\textbf{Site*Biocrust}} & & & & & & & & \\
        & SG \quad BSC+  & 62.7 \pm 21.2 & {(ab)}  & 44 \pm 16 & {(ab)} & 340 \pm 340 & {(bc)} & 7.5 \pm 5.7 & {(abc)} \\
        & SG \quad BSC--  & 67.5 \pm 20.6 & {(ab)}  & 54 \pm 18 & {(ab)} & 873 \pm 456 & {(d)}  & 16.7 \pm 7.1 & {(de)} \\
        & QdT \quad BSC+ & 87.3 \pm 37.5 & {(ab)}  & 38 \pm 15 & {(ab)} & 131 \pm 96 & {(ab)}  & 3.3 \pm 2.0 & {(abd)} \\
        & QdT \quad BSC-- & 70.1 \pm 18.7 & {(ab)}  & 42 \pm 18 & {(ab)} & 665 \pm 524 & {(cd)} & 15.8 \pm 10.2 & {(ce)} \\
        & LC \quad BSC+  & 85.8 \pm 67.1 & {(ab)}  & 45 \pm 20 & {(ab)} & 87 \pm 94 & {(a)}   & 2.1 \pm 1.9 & {(a)} \\
        & LC \quad BSC--  & 81.2 \pm 44.6 & {(ab)}  & 33 \pm 23 & {(ab)} & 395 \pm 344 & {(bc)} & 12.6 \pm 9.9 & {(bcde)} \\
        & NA \quad BSC+  & 380.4 \pm 329.5 & {(b)} & 19 \pm 23 & {(a)}  & 16 \pm 49 & {(a)}   & 5.2 \pm 19.9 & {(abcde)} \\
        & NA \quad BSC--  & 93.0 \pm 40.2 & {(a)}   & 69 \pm 45 & {(b)}  & 40 \pm 36 & {(a)}   & 0.9 \pm 1.2 & {(abcde)} \\
        \midrule
        \multicolumn{2}{@{}l}{\textbf{Significance} ($p$-value)} & & & & & & & & \\
        & Site         & \num{1.03e-05} & \tnote{*} & \num{0.0304} & \tnote{*} & \num{2.21e-14} & \tnote{*} & \num{1.93e-09} & \tnote{*} \\
        & Biocrust     & \num{0.01452} & \tnote{*} & \num{0.0034} & \tnote{*} & \num{4.37e-11} & \tnote{*} & \num{7.57e-10} & \tnote{*} \\
        & Site*Biocrust& \num{0.0166}  & \tnote{*} & \num{1.83e-05} & \tnote{*} & \num{0.00129}  & \tnote{*} & \num{0.000177} & \tnote{*} \\
        \midrule
        \multicolumn{2}{@{}l}{\textbf{Covariates}} &
        \multicolumn{2}{@{}l}{clay + C\textsubscript{T}} &
        \multicolumn{2}{@{}l}{silt + sand + N\textsubscript{T}} &
        \multicolumn{2}{@{}l}{} &
        \multicolumn{2}{@{}l}{\makecell[tl]{clay + sand + C\textsubscript{T} + \\ soil water content}} \\
        \bottomrule
      \end{tabular}
      \begin{tablenotes}[para,flushleft]
        \item[a] Letters indicate significant differences between means according to post-hoc tests with Šidák correction for multiple comparisons. Levels not sharing any letter are significantly different (p < 0.05).
        \item[*] Statistically significant effect (p < 0.05).
        \item[SD] Standard Deviation.
        \item[C\textsubscript{T}] Total Carbon content.
        \item[N\textsubscript{T}] Total Nitrogen content.
      \end{tablenotes}
    \end{threeparttable}
  \end{table}

  % ... text between tables ...

  % --- Table 2 Code (Percolation Fluxes) ---
  \begin{table}[htbp] % Changed from sidewaystable
    \centering
    \footnotesize % Reduced font size for the table
    \sisetup{separate-uncertainty = true, table-align-uncertainty = true}
    \begin{threeparttable}
      \caption{Percolating water fluxes on the study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover. Values correspond to mean $\pm$ standard deviation (SD) of five field replicates. A letter-based display of Šidák correction accompanies surface runoff parameters\tnote{a}, and the significance of the studied factor is shown as a p-value and list of covariates (C\textsubscript{T}, N\textsubscript{T}: total carbon and nitrogen content). Different letters indicate statistically significant different values based on our data, ns: non-significant.}
      \label{tab:percolation_fluxes}
      \setlength{\tabcolsep}{3pt} % Reduced further slightly

      \begin{tabular}{@{} l l S[table-format=3.0, table-figures-uncertainty=3] @{\,} c
                             S[table-format=2.1, table-figures-uncertainty=2] @{\,} c
                             S[table-format=2.0, table-figures-uncertainty=2] @{\,} c
                             S[table-format=1.1, table-figures-uncertainty=2] @{\,} c
                          @{}}
        \toprule
        \multicolumn{2}{@{}l}{\multirow{3}{*}{\textbf{Factor}}} &
        {\makecell{\textbf{Time to start}\\\textbf{percolation}\\\textbf{flow}}} & & % Added line break
        {\makecell{\textbf{Percolation}}} & &
        {\makecell{\textbf{Sediments in}\\\textbf{percolation}\\\textbf{flow}}} & & % Added line breaks
        {\makecell{\textbf{Sediment load}\\\textbf{in percolation}}} & \\ % Added line break
        \cmidrule(lr){3-3} \cmidrule(lr){5-5} \cmidrule(lr){7-7} \cmidrule(lr){9-9}
        \multicolumn{2}{@{}l}{} & {[\si{\second}]} & & {[\si{L.h^{-1}}]} & & {[\si{g.m^{-2}.h^{-1}}]} & & {[\si{g.L^{-1}.m^{-2}}]} & \\
        \midrule
        \multicolumn{2}{@{}l}{\textbf{Mean} $\pm$ \textbf{SD}} & & & & & & & & \\
        & Site \quad SG  & 223 \pm 190   &        & 18.0 \pm 14 & {(a)}  & 19 \pm 34 &        & 4.2 \pm 19.7 &       \\
        & \phantom{Site \quad} QdT & 175 \pm 94.5  &        & 22.8 \pm 15 & {(a)}  & 7 \pm 10  &        & 0.2 \pm 0.3  &       \\
        & \phantom{Site \quad} LC  & 234 \pm 183   &        & 22.4 \pm 13 & {(a)}  & 13 \pm 15 &        & 0.5 \pm 0.5  &       \\
        & \phantom{Site \quad} NA  & 145 \pm 169   &        & 65.0 \pm 39 & {(b)}  & 23 \pm 25 &        & 0.4 \pm 0.4  &       \\
        \addlinespace
        & Biocrust \quad BSC+ & 171 \pm 133   &        & 42.6 \pm 34 & {(b)}  & 19 \pm 22 & {(b)}  & 0.5 \pm 0.5  &       \\
        & \phantom{Biocrust \quad} BSC- & 218 \pm 190   &        & 21.5 \pm 21 & {(a)}  & 12 \pm 24 & {(a)}  & 2.1 \pm 13.7 &       \\
        \midrule
        \multicolumn{2}{@{}l}{\textbf{Site*Biocrust}} & & & & & & & & \\
        & SG \quad BSC+  & 202 \pm 103   &        & 24.8 \pm 15 & {(ab)} & 19 \pm 18 &        & 0.7 \pm 0.5  &       \\
        & SG \quad BSC-  & 244 \pm 251   &        & 11.1 \pm 10 & {(a)}  & 18 \pm 46 &        & 7.5 \pm 27.5 &       \\
        & QdT \quad BSC+ & 148 \pm 63.9  &        & 30.5 \pm 13 & {(b)}  & 9 \pm 13  &        & 0.3 \pm 0.3  &       \\
        & QdT \quad BSC- & 202 \pm 113   &        & 15.1 \pm 13 & {(ab)} & 5 \pm 6   &        & 0.2 \pm 0.2  &       \\
        & LC \quad BSC+  & 226 \pm 223   &        & 23.5 \pm 14 & {(ab)} & 17 \pm 19 &        & 0.6 \pm 0.5  &       \\
        & LC \quad BSC-  & 241 \pm 139   &        & 21.3 \pm 14 & {(ab)} & 9 \pm 9   &        & 0.4 \pm 0.3  &       \\
        & NA \quad BSC+  & 107 \pm 35.6  &        & 91.5 \pm 28 & {(c)}  & 30 \pm 32 &        & 0.4 \pm 0.4  &       \\
        & NA \quad BSC-  & 183 \pm 234   &        & 38.5 \pm 30 & {(b)}  & 16 \pm 15 &        & 0.4 \pm 0.3  &       \\
        \midrule
        \multicolumn{2}{@{}l}{\textbf{Significance} ($p$-value)} & & & & & & & & \\
        & Site         & \multicolumn{2}{c}{(ns)} & \num{1.78e-12} & \tnote{*} & \multicolumn{2}{c}{(ns)} & \multicolumn{2}{c}{(ns)} \\
        & Biocrust     & \multicolumn{2}{c}{(ns)} & \num{8.11e-08} & \tnote{*} & \num{0.00946} & \tnote{*} & \multicolumn{2}{c}{(ns)} \\
        & Site*Biocrust& \multicolumn{2}{c}{(ns)} & \num{0.00164} & \tnote{*} & \multicolumn{2}{c}{(ns)} & \multicolumn{2}{c}{(ns)} \\
        \midrule
        \multicolumn{2}{@{}l}{\textbf{Covariates}} &
        \multicolumn{2}{@{}l}{clay} &
        \multicolumn{2}{@{}l}{} &
        \multicolumn{2}{@{}l}{\makecell[tl]{clay + silt + sand +\\ C\textsubscript{T} + SOC}} &
        \multicolumn{2}{@{}l}{\makecell[tl]{clay + silt + sand\\ + C\textsubscript{T} + SOC}} \\
        \bottomrule
      \end{tabular}
      \begin{tablenotes}[para,flushleft]
        \item[a] Letters indicate significant differences between means according to post-hoc tests with Šidák correction for multiple comparisons. Levels not sharing any letter are significantly different (p < 0.05).
        \item[*] Statistically significant effect (p < 0.05).
        \item[ns] Non-significant (p >= 0.05).
        \item[SD] Standard Deviation.
        \item[C\textsubscript{T}] Total Carbon content.
        \item[N\textsubscript{T}] Total Nitrogen content.
        \item[SOC] Soil Organic Carbon.
      \end{tablenotes}
    \end{threeparttable}
  \end{table}
